Lens Modeling in \sw

### 2013-09-06 text/tex/spaghetti.tex
some changes

\section{\spl} \label{sec:SpaghettiLens}

@@

\section{The simulated lenses} \label{sec:sims}

Three kinds of sims.

\begin{itemize}
\item {\em Quasar:\/} A singular elliptical isothermal plus constant
  external shear, with a circular Gaussian source.
\item {\em Galaxy:\/} Lens as with quasar, but elliptical de
  Vaucouleurs source.
\item {\em Galaxy:\/} Lens is circular NFW plus one dominant
  elliptical SIE and perturbating elliptical SIEs, source as with
  galaxy.
\end{itemize}
Lenses follow \cite{2001astro.ph..2341K,2001astro.ph..2340K}.
Parameters in online supplement.

>>>>

\section {Setup} \label{sec:setup}

\subsection{\sw} \label{sec:SpaceWarps}
some words about \sw

\subsection{\spl} \label{sec:SpaghettiLens}

@@

\subsection{The simulated lenses} \label{sec:sims}

In order to estimate users performance, \sw included some simulated lensing configurations in their image set.

There are three kinds of simulated lenses:

\begin{itemize}
  \item {\em Quasar:\/} A singular elliptical isothermal plus constant
    external shear, with a circular Gaussian source.
  \item {\em Galaxy:\/} Lens as with quasar, but elliptical de
    Vaucouleurs source.
  \item {\em Galaxy:\/} Lens is circular NFW plus one dominant
    elliptical SIE and perturbating elliptical SIEs, source as with
    galaxy.
\end{itemize}
Lenses follow \cite{2001astro.ph..2341K,2001astro.ph..2340K}.
Parameters can be looked up in online supplement.

\subsection{The Test setup} \label{sec:testsetup}
We made use of this simulated lenses and further tested the volunteers abilities to model those simulated lensing images.

The testing was done with a small number of volunteers ($N_v=4$) and a set of simulated configurations (N_{sim}=30) chosen to represent some typical configurations.
\todo{witch??}

Two tests were done on the models created by the volunteers:

\begin{enumerate}
  \item Correct identification of extremal points
  \item Reproduction of the mass distribution of the lens
\end{enumerate}

The first test required the volunteers to accomplish 2 tasks: First to identify and distinguish lensed images from background light sources.
Second to come up with a logical ordering of the arrival time of those lensed images.

The second test compared the enclosed mass $\kappa(r)$ of the models and the simulations.
